An Analysis of Security Vulnerabilities in Container Images for Scientific Data Analysis

### 2020-10-26 paper.tex
Re-generated figures, fixed typos in p values

Unsurprisingly, a strong linear relationship is found between the number of
detected vulnerabilities and the number of packages present in the
image (Fig~\ref{fig:vulnerabilities}-\textbf{C}, r=0.82,
$p\textless10^{-12}$). On average, 1.7 vulnerabilities are introduced for
each new package installation. This observation motivates a systematic
review of software dependencies by application developers, to avoid
unnecessary packages in container images. This is also an argument in favor of lightweight
distributions such as Alpine. Compared to Ubuntu and Debian distributions,
CentOS images seem to have a lower number of vulnerabilities by package on
average, although data is too scarce to conclude.

@@

Updating container images reduces the number of vulnerabilities by package
by a factor of 3 on average, resulting in only 0.6 extra vulnerabilities by
package (Fig~\ref{fig:vulnerabilities}-\textbf{D}, r=0.81,
$p\textless10^{-8}$). Twelve container images are missing on this figure:
six of them could not be updated due to various issues with the package
manager, and six of them are Singularity images that we didn't update.
% \change{3 out of these missing 6 images retured an error while updating which
% indicates a problem with the package installer, 2 were unable to update because they
% reached EOL and last one with CentOS 7.1.1503 returned libselinux conflicts with systemd} 
In spite of the associated reproducibility challenges, updating
packages therefore appears to be an efficient way to avoid vulnerabilities. It
is not an ultimate solution though, as a substantial number of
vulnerabilities remain.

>>>>

Unsurprisingly, a strong linear relationship is found between the number of
detected vulnerabilities and the number of packages present in the
image (Fig~\ref{fig:vulnerabilities}-\textbf{C}, r=0.82,
$p\textless10^{-11}$). On average, 1.7 vulnerabilities are introduced for
each new package installation. This observation motivates a systematic
review of software dependencies by application developers, to avoid
unnecessary packages in container images. This is also an argument in favor of lightweight
distributions such as Alpine. Compared to Ubuntu and Debian distributions,
CentOS images seem to have a lower number of vulnerabilities by package on
average, although data is too scarce to conclude.

@@

Updating container images reduces the number of vulnerabilities by package
by a factor of 3 on average, resulting in only 0.6 extra vulnerabilities by
package (Fig~\ref{fig:vulnerabilities}-\textbf{D}, r=0.81,
$p\textless10^{-7}$). Twelve container images are missing on this figure:
six of them could not be updated due to various issues with the package
manager, and six of them are Singularity images that we didn't update.
% \change{3 out of these missing 6 images retured an error while updating which
% indicates a problem with the package installer, 2 were unable to update because they
% reached EOL and last one with CentOS 7.1.1503 returned libselinux conflicts with systemd} 
In spite of the associated reproducibility challenges, updating
packages therefore appears to be an efficient way to avoid vulnerabilities. It
is not an ultimate solution though, as a substantial number of
vulnerabilities remain.
